---
title: "assign4"
output: html_notebook
---


For the regular expression exercises, try writing first using regular expressions directly, then try using rverbalexpressions. Provide the code for both. 

# Part 1

```{r pkgs, message=FALSE}
library(tidyverse)
library(lubridate)
library(RVerbalExpressions)
```


## R4DS 16.4.5

Create a vector of dates giving the first day of every month in the current year. 
```{r}
ymd("2019-01-01") + months(0:11)
```

Write a function that given your birthday (as a date), returns how old you are in years.
```{r}
get_age <- function(bday) {
  (bday %--% today()) %/% years(1)
}

bday <- "1996-08-08"
get_age(ymd(bday))
```

Write a function that given your birthday, returns the day of the week you were born on. 

```{r}
get_bweek <- function(bday) {
  wday(bday)
}

get_bweek(bday = bday)
```


## R4DS 14.3.2.1

Given the corpus of common words in stringr::words, create regular expressions that find all words that have seven letters or more. (Since this list is long, you might want to use the match argument to str_view() to show only the matching or non-matching words.)

```{r}
words <- stringr::words


str_view_all(words,".......+", match = TRUE)

more_7 <- rx() %>%
  rx_start_of_line() %>%
  rx_word_char() %>% 
  rx_repeat_previous(7) %>%
  rx_anything() %>% 
  rx_end_of_line()

str_view(words,more_7, match = TRUE)
```



## R4DS 14.3.3.1

Use str_detect to find all words that:

That only contain consonants. (Hint: thinking about matching “not”-vowels.)
```{r}
only_co <- str_detect(stringr::words, "^[^aeiou]+$")
words[only_co]

ronly_cp <- rx() %>%
  rx_start_of_line() %>%
  rx_anything_but("aeiou") %>%
  rx_end_of_line() %>%
  grepl(words)

words[ronly_cp]


```

Empirically verify the rule “i before e except after c”.

The first result shows the rule might be true.
However, the second result tells us it is not true.

```{r}
length(str_subset(words, "(cei|[^c]ie)"))
length(str_subset(words, "(cie|[^c]ei)"))

```

In other words, if we find words that contain exactly cie, we can also empirically verify the rule “i before e except after c”.
```{r}
ev_rule <-rx() %>%
  rx_find("cie")
  
words[str_detect(words,ev_rule)]

```

Create a regular expression that will match telephone numbers as commonly written in the US. Split this up into multiple expressions as needed.


```{r}
cellnum <- c("879-154-7908", "135.484.7895","13547984587")
str_view(cellnum,"\\d{3}-\\d{3}-\\d{4}|\\d{3}.\\d{3}.\\d{4}")

telrx <- rx() %>%
  rx_start_of_line() %>%
  rx_digit() %>%
  rx_repeat_previous(3) %>%
  rx_any_of("-.") %>%
  rx_digit() %>%
  rx_repeat_previous(3) %>%
  rx_any_of("-.") %>%
  rx_digit() %>%
  rx_repeat_previous(4) %>%
  rx_end_of_line()

str_view(cellnum, telrx)
```


# Part 2


Choose a dataset (this can be the same dataset as the last assignment, or a new one). Define a predictive modeling problem. Create the appropriate files and notebooks to do the following:

1. Describe the data and the problem

2. Read in and check data

2. Clean up the data. 

*Note: You may request that score for these sections replace your score for the coding portion of Assignment 3.*

4. Using best practices, write four functions which add engineered features to the dataset, including a description and rationale. Include a test to determine whether the features are working as intended. 

5. Prepare the data for modeling

Note: this will form the basis for your midterm project. Take advantage of TA's and my office hours. We can provide feedback and guidance. 

