---
title: "10-import"
output:
  html_document:
    df_print: paged
  pdf_document: default
---
# Describe the data and the problem

I am interested in predicting the housing Values in Suburbs of Boston.

We have the some interesting features of the house, for instance, 



$black$

1000(Bk - 0.63)^2 where Bk is the proportion of blacks by town.

$ptratio$

pupil-teacher ratio by town.

How would these enviornment variables affect a house's value?

The medv variable is the target variable.

The Boston data frame has 506 rows and 14 columns.

This data frame contains the following columns:

crim

per capita crime rate by town.

zn

proportion of residential land zoned for lots over 25,000 sq.ft.

indus

proportion of non-retail business acres per town.

chas

Charles River dummy variable (= 1 if tract bounds river; 0 otherwise).

nox

nitrogen oxides concentration (parts per 10 million).

rm

average number of rooms per dwelling.

age

proportion of owner-occupied units built prior to 1940.

dis

weighted mean of distances to five Boston employment centres.

rad

index of accessibility to radial highways.

tax

full-value property-tax rate per $10,000.

ptratio

pupil-teacher ratio by town.

black

1000(Bk - 0.63)^2 where Bk is the proportion of blacks by town.

lstat

lower status of the population (percent).

medv

median value of owner-occupied homes in $1000s.

I found this data set from our class repo, more information could be found at https://www.kaggle.com/c/boston-housing/overview/description

## loading pkgs
```{r pkgs, message=FALSE}
library(tidyverse)
library(ggplot2)
library(fs)
library(purrr)
library(stringr)
library(assertr)
library(caret)
```

## load data

```{r load data, message=FALSE}
df <- read_csv("./data/BostonHousing.csv")
```
## some functions
```{r functions}
#for check how many unique values for each var.
col_uni <- function(df){
  map(
    map(df,unique), # apply the unique function to each column, return the unique value of each column.
    length)
}
```


## overview

Information about our dataset. 
From the tables below, we can find that we dont have missing values in our dataset and the colnames of our dataset are cleaning enough.


```{r #dataoverview}
dim(df)
str(df)
#no need for clean_names()
#no need for na.omit()

```
## check the dataset
```{r check}
# Doule check how many missing values in our dataset
sum(is.na(df))
#no need for dealing with NAs. 

# check the limit (based on description) for each variable 
df %>% 
  assert(in_set(c(1, 0)), chas)%>% 
  assert(in_set(c(0:24)), rad)%>% 
  assert(within_bounds(0,1), nox) %>%
  assert(within_bounds(0,100), zn)%>%
  assert(within_bounds(0,100), crim)%>%
  assert(within_bounds(0,Inf),indus)%>%
  assert(within_bounds(0,120), age) %>%
  assert(within_bounds(0,Inf), dis) %>%
  assert(within_bounds(0,100), ptratio) %>%
  assert(within_bounds(0,Inf), tax) %>%
  assert(within_bounds(0,Inf), medv) %>%
  assert(within_bounds(0,Inf), b) %>%
  assert(within_bounds(0,100), lstat)
```

## check each var

From the result below, we can find that there are some variables only have few unique values. 
they may be factor instead of numeric.

"rad" & "chas" should be factor variables.
```{r check var}
col_uni(df)
```
