---
title: "10-import"
output:
  html_document:
    df_print: paged
  pdf_document: default
---
# Describe the data and the problem

I am interested in predicting the housing Values in Suburbs of Boston.

We have the some interesting features of the house, for instance, 

$black$
1000(Bk - 0.63)^2 where Bk is the proportion of blacks by town.

$ptratio$
pupil-teacher ratio by town.

How would these enviornment variables affect a house's value?


I found this data set from our class repo, more information could be found at https://www.kaggle.com/c/boston-housing/overview/description

## loading pkgs
```{r pkgs, message=FALSE}
library(tidyverse)
library(ggplot2)
library(fs)
library(purrr)
library(stringr)
library(assertr)
library(caret)
```

## load data

```{r load data, message=FALSE}
df <- read_csv("./data/BostonHousing.csv")
```
## some functions
```{r functions}
#for check how many unique values for each var.
col_uni <- function(df){
  map(df,unique)
}
```


##overview
```{r #dataoverview}
dim(df)
str(df)
summary(df)
```
## check the dataset
```{r check}
# check how many missing values in our dataset
sum(is.na(df))



# check the limit (based on description on the kaggle) for each variable 
df %>% 
  assert(in_set(c(1, 0)), chas)%>% 
  assert(in_set(c(0:24)), rad)%>% 
  assert(within_bounds(0,1), nox) %>%
  assert(within_bounds(0,100), zn)%>%
  assert(within_bounds(0,100), crim)%>%
  assert(within_bounds(0,Inf),indus)%>%
  assert(within_bounds(0,120), age) %>%
  assert(within_bounds(0,Inf), dis) %>%
  assert(within_bounds(0,100), ptratio) %>%
  assert(within_bounds(0,Inf), tax) %>%
  assert(within_bounds(0,Inf), medv) %>%
  assert(within_bounds(0,Inf), b) %>%
  assert(within_bounds(0,100), lstat)
```

## check each var

From the result below, we can find that there are some variables only have few unique values. 
they may be factor instead of numeric.

"rad" & "chas" should be factor variables.
```{r check var}
map(col_uni(df),length)
```
