---
title: "30-feature engineering"
output:
  html_document:
    df_print: paged
---
4. Using best practices, write four functions which add engineered features to the dataset, including a description and rationale. Include a test to determine whether the features are working as intended. 
## loading pkgs
```{r pkgs, message=FALSE}
library(tidyverse)
library(ggplot2)
library(fs)
library(purrr)
library(stringr)
library(assertr)
library(caret)
```

## check each var

From the result below, we can find that there are some variables only have few unique values. 
they may be factor instead of numeric.

"rad" & "chas" should be factor variables.
```{r checkvar}
col_uni <- function(df){
  map(df,unique)
}

map(col_uni(df),length)
```

###1,Turn chas and rad into factors.

We need to let R know that these variables are factors instead of numeric.
```{r vartofactor}
tof <- function(x) (as.factor(x))

tofactor <- function(df,var){
  df %>%
    mutate_at(var, list(fc = tof))
}

df <- tofactor(df,c("rad","chas"))

#test
is.factor(df$chas_fc)
is.factor(df$rad_fc)
```


###2,standardize

standardize numeric variables sometimes will make the prediction better.
```{r std}
scale2 <- function(x, na.rm = FALSE) (x - mean(x, na.rm = na.rm)) / sd(x, na.rm = na.rm)
dfstd <- function(df,var){
  df %>% 
    mutate_at(var, list(std = scale2))
}

df <- dfstd(df,var = c("crim" ,"zn","indus","nox", "rm", "age", "dis","tax","ptratio", "b", "lstat", "medv"))

#test
df %>%
  select(contains("_std"),everything())
```
###3, level of crime rate(in tidyverse)
```{r levelcrime}
summary(df$crim)
crime_level <- function(df) {
  df %>% 
    mutate(crim_level = case_when(
      crim <= 0.09 ~ "low",
      crim <= 3.7 ~"medium",
      TRUE ~ "high"
    ))
}

df <- crime_level(df)
#test
unique(df$crim_level)
```


###4, try to cut ptratio variable into different level.(not in tidyverse)

$ptratio$
pupil-teacher ratio by town.

I want to cut the variables into 3 level, low, median, high. As in the realworld, when people consider about the education they always use level instead of numbers. 

```{r levelptratio}

summary(df$ptratio)

cutptratio <- function(x){
  if(x <= 17.4){
    x = "low"
  }else{
    if(x >= 20.2){
      x = "high"
    }else{
      x = "Median"
    }
  }
}



for (i in 1:506) {
  df$ptratio_cut[i] <- cutptratio(df$ptratio[i])
}

unique(df$ptratio_cut)
```

## Prepare the data for modeling

split the training and testing set
```{r train/test split}
set.seed(2019)

trainIndex <- createDataPartition(df$medv, p = .75, list = FALSE)

df_tr <- df[trainIndex,]
df_test <- df[-trainIndex,]

```

